Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 inspiral_svd.tex
Renamed analysis.tex to implementation.tex
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@893 ccdd05d5-56c1-461a-bf98-85f6876523b4
Keywords not needed
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@894 ccdd05d5-56c1-461a-bf98-85f6876523b4
Moved NSF fellowship to end of acknowledgements
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@900 ccdd05d5-56c1-461a-bf98-85f6876523b4
merged
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@911 ccdd05d5-56c1-461a-bf98-85f6876523b4
fixed we
git-svn-id: h

\title[LLOID]{Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy}

@@

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for multi-messenger astronomy.  Prompt detection alerts to the astronomical community may make it possible to observe the onset of electromagnetic emission from compact binary coalescence.  We demonstrate a computationally practical analysis strategy that produces early warning triggers even before gravitational radiation from the final merger has arrived at the detectors.  With current rate estimates for the Advanced \LIGO{} design configuration, we should detect $\sim$10 sources earlier than 10 seconds before merger in 1 year of live time.
\end{abstract}

@@

%\keywords{Gravitational Waves, Laser Interferometry}

@@

\input{analysis}

@@

\ack{\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}.  This research is supported by the National Science Foundation through a Graduate Research Fellowship to LS.  CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection.  CH
would also like to thank Patrick Brady for countless fruitful conversations
about low latency analysis methods.  NF would like to thank Alessandra Corsi
for illuminating discussions on astronomical motivations.

>>>>

\title[LLOID]{Technique for \earlywarning\ detection of compact binary
coalescence and its implications for multi-messenger astronomy}

@@

\begin{abstract}
The rapid detection of compact binary coalescence with a network of advanced
gravitational-wave detectors will offer a unique opportunity for
multi-messenger astronomy.  Prompt detection alerts to the astronomical
community may make it possible to observe the onset of electromagnetic emission
from compact binary coalescence.  We demonstrate a computationally practical
analysis strategy that produces early warning triggers even before
gravitational radiation from the final merger has arrived at the detectors.
With current rate estimates for the Advanced \LIGO{} design configuration, it
should be possible to detect $\sim$10 sources earlier than 10 seconds before
merger in 1 year of live time.
\end{abstract}

@@

@@

\input{implementation}

@@

\ack{\LIGO\ was constructed by the California Institute of Technology and
Massachusetts Institute of Technology with funding from the National Science
Foundation and operates under cooperative agreement
\textsc{phy}-\oldstylenums{0107417}.  CH would like to thank Ilya Mandel for
many discussions about rate estimates and the prospects of early detection.  CH
would also like to thank Patrick Brady for countless fruitful conversations
about low latency analysis methods.  NF would like to thank Alessandra Corsi
for illuminating discussions on astronomical motivations.  This research is supported by the National Science Foundation through a Graduate Research Fellowship to LS.
